### 2019-04-07 papers/journal/related.tex
Uniform use of the title without :
Section 8 completed

Previous analysis of vesicle traffic system has used simulation and statistical reasoning~\cite{mani2016stacking}. 
%
Such analysis is far from complete and can only make statistical claims about VTS based on a subset of samples. 
%
The properties of VTS discussed in this paper require precise analysis for all possible rules and variations, that make formal methods a suitable alternative.

The Boolean satisfiabilty (SAT) solvers are used to solve wide range of problems including
%
software and hardware verification~\cite{biere1999symbolic1, biere1999symbolic2, bjesse2001finding, velev2003effective}, equivalence checking~\cite{goldberg2001using}, automatic test case generation~\cite{stephan1996combinational},
AI planning~\cite{kautz1996pushing} and scheduling~\cite{gomes1998randomization}. 
%
The enormous progress in the performance of SAT and SMT solvers
%Improvement in SAT and SMT solvers
in the past decades have led to their use in modeling and understanding complex biological systems~\cite{heule2010exact,yordanov2013smt,mangla2010timing}. 
%
Many of which involve reasoning about graphs and networks rules~\cite{guerra2012reasoning,chin2008biographe} with possible exhaustive search.
% and hence can be reduced to solving a SAT/SMT question. 
%

@@

We have extended the application of SAT and SMT solvers to a comparatively more complex biological transport network~\cite{mani2016stacking} namely vesicle traffic system (VTS). 
%
%Unlike the GNR, not many  VTS
We have presented both SAT and SMT based encoding for our Boolean model of the VTS.
%
We have also introduced the use of QBF solvers and it's encoding in this context.
% 
To our best knowledge our work is the first application
of formal methods to the vesicle traffic networks.

In recent years, there has been a wide range of methods
developed for the similar synthesis problems~\cite{sketch,sygus,exampleSynth}.
%
They range from filling gaps an implementation of C programs from the pool of template predicates to learn a program from example
runs of the program.
%
In the course of developing such methods,
the background technology, i.e. solving of quantified
constraints has been evolving rapidly~\cite{lonsing2010depqbf,z3Quant}.
%

There has been some work in
applying synthesis technique in biology especially in gene regulatory networks~\cite{shavit2016automated, fisher2015synthesising}. A very recent work~\cite{fisher2015synthesising} synthesize executable gene regulatory networks from single-cell gene expression data.
Synthesis technique is also used in optimal synthesis for chemical reaction networks~\cite{cardelli2017syntax}. The~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques for the synthesis whereas ~\cite{shavit2016automated} uses SMT for synthesis. The paper~\cite{cardelli2017syntax} in addition to using SMT over ODE, uses a template-guided approach. In our case queries contain quantifiers so we have employed QBF solving with Z3 for the solving the synthesis problem. To our best knowledge, this is the first application of synthesis in VTS.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
~

>>>>

\noindent \improve{Not upto the mark}The previous analysis of vesicle traffic system used simulation and statistical reasoning~\cite{mani2016stacking}. 
%
Such analysis is far from complete and can only make statistical claims about VTS based on a subset of samples. 
%
The properties of VTS discussed in this paper require precise analysis for all possible rules and variations, that make formal methods a suitable alternative.

The Boolean satisfiability (SAT) solvers are used to solve a wide range of problems including
%
software and hardware verification~\cite{biere1999symbolic1, biere1999symbolic2, bjesse2001finding, velev2003effective}, equivalence checking~\cite{goldberg2001using}, automatic test case generation~\cite{stephan1996combinational},
AI planning~\cite{kautz1996pushing} and scheduling~\cite{gomes1998randomization}. 
%
The enormous progress in the performance of SAT and SMT solvers
%Improvement in SAT and SMT solvers
in the past decades have led to their use in modeling and understanding complex biological systems~\cite{heule2010exact,yordanov2013smt,mangla2010timing}. 
%
Many of which involve reasoning about graphs and networks rules~\cite{guerra2012reasoning,chin2008biographe} with possible exhaustive search.
% and hence can be reduced to solving a SAT/SMT question. 
%

@@

We have extended the application of SAT and SMT solvers to a comparatively more complex biological transport network~\cite{mani2016stacking} namely vesicle traffic system (VTS). 
%
We have presented both SAT and SMT based encoding for our Boolean model of the VTS.
%
We have also introduced the use of QBF solvers and it's encoding in this context.
% 
To our best knowledge, this series of work is the first application
of formal methods to the vesicle traffic networks.

In recent years, there has been a wide range of methods
developed for similar synthesis problems~\cite{sketch,sygus,exampleSynth}.
%
They range from filling gaps an implementation of C programs from the pool of template predicates to learn a program from the example
runs of the program.
%
In the course of developing such methods,
the background technology, i.e. solving of quantified
constraints has been evolving rapidly~\cite{lonsing2010depqbf,z3Quant}.
%

There has been some work in applying synthesis technique in biology especially in gene regulatory networks~\cite{shavit2016automated, fisher2015synthesising}. A very recent work~\cite{fisher2015synthesising} synthesize executable gene regulatory networks from single-cell gene expression data.
Synthesis technique is also used in optimal synthesis for chemical reaction networks~\cite{cardelli2017syntax}. The~\cite{fisher2015synthesising} uses constraint (satisfiability) solving techniques for the synthesis whereas ~\cite{shavit2016automated} uses SMT for synthesis. The paper~\cite{cardelli2017syntax} in addition to using SMT over ODE, uses a template-guided approach. In our case queries contain quantifiers so we have employed QBF solving with Z3 for solving the synthesis problem. To our best knowledge, this is the first application of synthesis in VTS.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
~
